Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-01-06 manuscript/manuscript.Rmd
improved intro

Introduction
------------
Population models are important tools for predicting the impacts of environmental change on species. But reconciling the scales at which population models are parameterized and the scales at which environmental changes play out remains a challenge [@Freckleton2011; @Queenborough2011]. The major hurdle is that most population models, at least for plant species, are built using data from small, localized plots because parameterizing traditional population models requires tracking the fates of individuals. These models are difficult to scale up from the micro to meso-scales because the fitted parameters do not fully represent the spatial variation present at scales beyond that at which the data are collected [@Sæther2007]. Thus, our ability to use population models to predict the consequences of climate change is limited when we rely on individual-level data.

@@

Basing population models on population- rather than individual-level data in a climate change context is hampered by the fact that it is individuals that respond to climate, not populations [@Clark2012]. This fact puts us in uneasy proximity to an "ecological fallacy" where one deduces inference on the individual from statistical inference on the group [@PIANTADOSI1988].

@@

>>>>

Introduction
------------
Population models are important tools for predicting the impacts of environmental change on species. But reconciling the scales at which population models are parameterized and the scales at which environmental changes play out remains a challenge [@Clark2010; @Freckleton2011; @Queenborough2011; @Clark2012]. The major hurdle is that most population models, at least for plant species, are built using data from small, localized plots because parameterizing traditional population models requires tracking the fates of individuals. These models are difficult to scale up from the micro to meso-scales because the fitted parameters do not fully represent the spatial variation present at scales beyond that at which the data are collected [@Sæther2007]. Thus, our ability to use population models to predict the consequences of climate change is limited when we rely on individual-level data.

@@

Basing population models on aggregated individual-level data in a climate change context is hampered by the fact that it is individuals that respond to climate, not populations [@Clark2012]. This fact puts us in uneasy proximity to an "ecological fallacy" where one deduces inference on the individual from statistical inference on the group [@PIANTADOSI1988]. For example, individual plants may respond positively to precipitation but a negative trend is observed at the population level due to increased competition among plants as they grow larger and consume more resources. Thus, it is important to ask the question: Can aggregated data be used to detect climate signals of the same sign and magnitude as individual-level data? If not, then building population models with climate covariates on aggregated data will lead to incorrect forecasts.

Here, we test the hypothesis (idea?) that statistical and population models based on aggregated data can detect climate signals as wells as models based on individual-level data. We use a unique demographic dataset that tracks the fates of individual plants from four species to build single-species population models, since those are often used tools for ecological forecasts and climate vulnerability assessments. We first fit population models with interannual variation in vital rates explained, in part, by climate covariates. We then perturb the climate covariates to test the sensitivities of species to climate change. By doing these analyses using both individual and aggregated forms of the same data, we provide a rigorous test of our hypothesis. We find that...

@@

\pagebreak{}

### 2015-01-06 manuscript/manuscript.tex
improved intro

Population models are important tools for predicting the impacts of
environmental change on species. But reconciling the scales at which
population models are parameterized and the scales at which
environmental changes play out remains a challenge (Freckleton et al.
2011, Queenborough et al. 2011). The major hurdle is that most
population models, at least for plant species, are built using data from
small, localized plots because parameterizing traditional population
models requires tracking the fates of individuals. These models are
difficult to scale up from the micro to meso-scales because the fitted
parameters do not fully represent the spatial variation present at
scales beyond that at which the data are collected (Sæther et al. 2007).
Thus, our ability to use population models to predict the consequences
of climate change is limited when we rely on individual-level data.

@@

Basing population models on population- rather than individual-level
data in a climate change context is hampered by the fact that it is
individuals that respond to climate, not populations (Clark et al.
2012). This fact puts us in uneasy proximity to an ``ecological
fallacy'' where one deduces inference on the individual from statistical
inference on the group (Piantadosi et al. 1988).

@@

>>>>

Population models are important tools for predicting the impacts of
environmental change on species. But reconciling the scales at which
population models are parameterized and the scales at which
environmental changes play out remains a challenge (Clark et al. 2010,
2012, Freckleton et al. 2011, Queenborough et al. 2011). The major
hurdle is that most population models, at least for plant species, are
built using data from small, localized plots because parameterizing
traditional population models requires tracking the fates of
individuals. These models are difficult to scale up from the micro to
meso-scales because the fitted parameters do not fully represent the
spatial variation present at scales beyond that at which the data are
collected (Sæther et al. 2007). Thus, our ability to use population
models to predict the consequences of climate change is limited when we
rely on individual-level data.

@@

Basing population models on aggregated individual-level data in a
climate change context is hampered by the fact that it is individuals
that respond to climate, not populations (Clark et al. 2012). This fact
puts us in uneasy proximity to an ``ecological fallacy'' where one
deduces inference on the individual from statistical inference on the
group (Piantadosi et al. 1988). For example, individual plants may
respond positively to precipitation but a negative trend is observed at
the population level due to increased competition among plants as they
grow larger and consume more resources. Thus, it is important to ask the
question: Can aggregated data be used to detect climate signals of the
same sign and magnitude as individual-level data? If not, then building
population models with climate covariates on aggregated data will lead
to incorrect forecasts.

Here, we test the hypothesis (idea?) that statistical and population
models based on aggregated data can detect climate signals as wells as
models based on individual-level data. We use a unique demographic
dataset that tracks the fates of individual plants from four species to
build single-species population models, since those are often used tools
for ecological forecasts and climate vulnerability assessments. We first
fit population models with interannual variation in vital rates
explained, in part, by climate covariates. We then perturb the climate
covariates to test the sensitivities of species to climate change. By
doing these analyses using both individual and aggregated forms of the
same data, we provide a rigorous test of our hypothesis. We find
that\ldots{}

@@

Clark, J. S., D. Bell, C. Chu, B. Courbaud, M. Dietze, M. Hersh, J.
HilleRisLambers, I. Ibáñez, S. LaDeau, S. McMahon, J. Metcalf, J. Mohan,
E. Moran, L. Pangle, S. Pearson, C. Salk, Z. Shen, D. Valle, and P.
Wyckoff. 2010. High-dimensional coexistence based on individual
variation: a synthesis of evidence. Ecological Monographs 80:569--608.
